\documentclass[oneside]{book}
\begin{document}
	\chapter{Aminor}
	The continent \textit{Aminor} is made up of five countries, the \textit{Khalinor} desert, the \textit{Greenlands}, the \textit{Icelands of Malin Kharr}, the \textit{Mountains of Ghamor} and the rocky \textit{Draken Islands}. 
	The different countries are all seperated by the \textit{Amin} sea, which is in the center of the continent. 
	\textit{Aminor's} borders are defined by the vast oceans that expand on every side of the continent and seem to have no end.
	In fact the people of Aminor have never crossed the sea, that surrounds their continent and don't know what, if anything lies beyond the vast blue oceans. 
	Only legends tell from the strange lands that may lay there. 
	The population consists mostly of humans, elves, eladrin and dwarves, which all have their own kingdoms and empires in their countries. 
	Other races like halflings and dragonborn also live here, but they mostly live among the humans and sometimes on their own, away from civilisation.
	
	\chapter{Khalinor}
	In the South East of Aminor there is the vast desert wasteland known as Khalinor. 
	Only few people live there and those who do mostly only live at the rims of the country and the only oasis in the desert \textit{Timi'in Ged}, where there are some strips of fertile land. 
	The inland of the country is only inhibited by the creatures of the desert to whom many adventurers have fallen prey and some fearless travellers not all of which have been seen again after they have entered. 
	Khalinor is also the least populated country apart from the Icelands and the Draken Islands which both don't have any population to speak of. 
	The city of \textit{Mouarak} lies at the delta of the river \textit{Silya} and has one of the biggest harbours in Aminor. 
	This harbour is also the only reliable connection between the other countries and Khalinor. 
	The only other harbour in Khalinor fit for international trade is the harbour of \textit{Tulruk} which is mostly used for smugglers who use the far eastern city as an outpost, where they can easily escape to the open sea.
 
	\section{Timi'in Ged}
	In the oasis of Timi'in Ged there are many people dwelling at the border of the desert.
	In order to keep the oasis from drying out threatening the lives of every inhibitants of Khalinor many wizards live here and perform various rituals battling against the forces of nature.
	As a result this place is loaded with magic energy and spells performed in and around the oasis have much more potency than when performed somewhere else. 
	The biggest city in Timi'in Ged, \textit{Saldary} even contains one of the two magic universities in Aminor, \textit{Malin'dur}.
	Other notable cities in Timi'in Ged are \textit{Sumarika}, the capital of Khalinor, \textit{Baljar}, the biggest trade outpost on the continent and 
	\textit{Kaa'nugar}, the only city in Aminor where most of the population are Dragonborn, because when they fleed from the slavery of the dragons the city took them all in.
	
	\section{Garra'bor and Karra'bor}
	The towns Karra'bor and Garra'bor are located in the North-East of Khalinor.
	A long time ago only Garra'bor existed, but after a civil war part of the population moved from the Garra'bor island to the mainland  and founded Karra'bor. 
	For a long time the two towns were in deep hatred towards each other, but nowadays they are friendly again and are even trading partners
	
	\section{Maviara Bay}
	In the North of Khalimor there is a big bay named \textit{Maviara Bay} after the two cities contained in it, \textit{Mavior} and \textit{Aradar}. 
	A long time ago this bay had the biggest harbours of Aminor and a flourishing economy. But one day a war between Aradar and Mavior broke out. 
	Ever since then Maviara Bay has been a danger zone for whoever sets foot in it and Mavior and Aradar stay at war for centuries.
	
	\section{Valley of Death}
	In the North of Khalimor there is a valley called the \textit{Valley of Death}. 
	This is the most dangerous place in all of Khalinor, with temperatures ranging from burning hot at day to freezing cold at night. 
	Only the temperatures have been the death of many unsuspecting wanderers. But this isn't the only danger of the Valley of Death.
	Various creatures live here and whoever is unlucky enough to meet any of them has most likely finished his life.
	
	\chapter{Mountains of Ghamor}
	These mountains are inhibited by the race of the dwarves, who mostly keep to themselves and only allow non-dwarves to live among them if they earned the respect of the clan. 
	Some of the dwarves leave the mountains though, those who want to see the world and don't want to become miners or blacksmiths.
	Because there is almost no vegetation or animals in the mountains, the dwarves of Ghamor are dependent on goods delivered from the outside world to the only dwarven overworld city of \textit{Orvik}.
	The five highest mountains here are the homes of the five stronges clans and are named by the founding family.
	\textit{Bronzeforge}, the highest mountain of Ghamor is also the home of the most influential dwarfen clan. 
	This clan has led the dwarven armies in the \textit{Great War} and since then has enjoyed big respect among the dwarves.
	In the three smaller mountains \textit{Dragonscale}, in the west, where the first dragonscale armor was made,
	\textit{Thunderaxe}, in the south, famous for their axes and \textit{Stonecrusher}, in the north, where the deepest mines have been dug, the other clans live, mostly independent from one another.
	The last and smallest of the important dwarvish clans lives in the North-East of Ghamor, in the mountain of \textit{Bronzebane}.
	This clan was once part of Bronzeforge but was banished from the mountain, after trying to overthrow the king.
	They are very disliked among the other dwarves and even other races, still plan to attack Bronzeforge again and have their own trading route for foreign goods, somewhere unknown in the far North of Ghamor, where they trade with the smugglers of Tulruk.
	
	\chapter{Draken Islands}
	The islands in the North-West of Aminor are called the Draken Islands.
	The only creatures, that live here are dragons, wyverns and similar animals. Many mountains here seem to be volcanoes, but not much research has been done, so it's unsure.
	Not much more is known about these islands. There is an outpost of civilisation here though.
	Adventurers, researchers, that want to know more about the wildlife here and wizards, what want free land to try dangerous spells come and live here.
	But the islands are still very dangerous and not all of the daring people coming here return to their homes.
	
	\chapter{Icelands of Malin Karr}
	In the far North of Aminor, there are the Icelans of Malin Karr. Here lives even less than on the Draken Islands. No animals or plants can survive in this place. 
	There was once a wizard named Malin Karr, that had enough power to survive in this cold. He lived here and build up an army of the Undead and demons in secret.
	When he was done he attacked the other countries in the war which is known as the Great war, after which huge portions of the population of Aminor were killed.
	Legend says ruins of his work can still be found in the Icelands.
	
	\chapter{Greenlands}
	The biggest and most populated country in Aminor are the Greenlands,in the South-West of Aminor, most of which is covered by the \textit{Fey} forest.
	In the North East of the Greenlands there is the \textit{Ballick valley} and in the South East the \textit{Sowgill Lake}.
	In the far South there is also an Island group, the \textit{Grendale islands}. Apart from those places, the Greenlands don't have many big cities.
	The cities there are are \textit{Aldskull}, that stands in direct contact with the outpost on the Draken islands. It is the only reliable way to get there and to return from the islands.
	It is also one of the three politically relevant cities in the Greenlands with the capital, \textit{Kingsrend} and the southern city of \textit{Linbrough}, at the river of \textit{Jall River}
	the smallest of the three and also the least relevant.
	These cities all rule over one third of the Greenlands.
	In the West there is the city of \textit{Awalock}, where explorers gather to try and find other continents in the west, after there have been rumors of people coming to Aminor over the sea from the West. 
	So far no one has ever reached another place in this direction, because the waters in the West were to dangerous to travel too far out.
	The other city in the West \textit{Windwarder}, where the river \textit{Bogrib} leaves the Fey, is at the border of the Fey and was founded in order to better the relationship
	between the elven races and the rest of the world, to great success.
	While the elves are still keeping mostly to themselves, and are still not trusting the dwarves nowadays there are trading routes to and from the Fey and many elves are now well-respected among other races and vice-versa.
	The biggest city in the East of the Greenlands, not located in the Ballick valley or around Sowgill Lake is the city of \textit{Blackwater}, at a point, two rivers flow into Jall River.
	In the north there is another big river, the \textit{Blog River}
	
	\section{Ballick valley}
	This is the main hub of magic in Aminor. The presence of magic is so vibrant, the rivers \textit{Bildor creek} and Jall river flow out of the valley, to higher altitudes.
	In the valley's center there is the city of \textit{Alwador} where the bigger of the two magic universities is located.
	Almost every wizard has studied here at one point in his life and many respectable wizards continue to work here and drive the reasearch on magic forward.
	In this valley there are also the cities of Kingsrend, the capital of the Greenlands, where most political decisions are made,
	and \textit{Murakar}, one of the oldest cities of the Greenlands. Here there is the famous library of Murakar where most of the available information in Aminor is kept.
	This city even predates the Great War.
	
	\section{Sowgill Lake}
	This is the largest lake on the whole continent, and it is not known how deep it is or which creatures dwell in its depths.
	Around this lake most of the Greenland population is centered. There are 4 major cities around the lake.
	\textit{Plywell} \textit{Caterick} \textit{Bellick} and \textit{Orvon}
	Plywell, located at the coast is an important trade harbours of the Greenlands and one of the most diverse cities on the whole continent, because historically, most refugees have been accepted in this city
	The two cities Caterick and Bellick are located on the two sides of where Jall River mounds into Sowgill Lake.
	They are known for their combined fishing and shipping industries they have been building up for centuries with combined knowledge from both sides of the river.
	At the border of the Fey, the city of Orvon is another city that tries to improve relations between elven races and the rest of the world.
	Successes here have been even more promising than up North with some elves and eladrin even living here. This is also where the first Half-elves are said to come from.
	There are also many other, smaller towns and cities located around this lake, 	many more than in the rest of the country.
	
	\section{Grendale islands}
	The Grendale islands are the \textit{Bolar} \textit{Baltar} \textit{Brunken} and \textit{Bergar}.
	These islands have a very warm climate and are where the top 1 per cent of the population live. You either have to be very lucky or very rich to get a home here.
	On Bolar there is the capital of the islands \textit{Boron}. This place is even more epxensive than the rest of the islands. 
	Except for Balton, which is considered the most expensive city on the whole contintent, there are no bigger cities on these islands.
	The rich like to live mostly on their own, so most houses are far apart here.
	Whoever lives in \textit{Balton} is not only part of the 1 per cent, but also of the 1 per cent of the 1 per cent. That's how rich they are.
	
	\section{Fey}
	This is the big forest covering most of the Greenlands. In here live the elves and eladrin, who mostly keep to themselves and do not welcome many visitors in their woods.
	They don't have actual cities or towns in this forest, but scattered settlements in the trees, which can sometimes switch position.
	People, that don't know the Fey to their heart and have no guide to lead them, can easily die from the wild animals that live here.
	In the center of the Fey there is the \textit{Kaja'ar tree}, a tree that is holy to elves and eladrin and is said to have magical powers. 
	The elves and Eladrin have had bad blood in the past, but after they had to unite during the Great War the two races have grown together and don't differ much anymore apart from their looks.
	
	\chapter{Glossary}
	Aminor = continent\\
	Amin = sea in which all the Aminor countries lie in\\
	Khalinor = desert in the South East of Aminor\\
	Greenlands = biggest country of Aminor, in the South West. Contains the Fey\\
	Icelands of Malin Kharr = Icy Wastelands ifn the North of Aminor\\
	Draken Islands = Rocky group of islands North of the Greenlands. Mostly populated by dragons and wyverns\\
	Mountains of Ghamor = mountainous country in the North East of Aminor mostly populated by dwarves\\
	Timi'in Ged = the only oasis in Khalinor\\
	Saldary = Biggest city in Timi'in Ged, contains the magic university Malin'dur\\
	Malin'dur = One of the two magic universities in Aminor\\
	Sumarika = the capital of Khalinor\\
	Baljar = city in Timi'in Ged, biggest trade outpost on the continent\\
	Kaa'nugar = city in Timi'in Ged, only city populated mostly by Dragonborn\\
	Silya = only river in Khalinor\\
	Tulruk = bandit city in the East of Khalinor\\
	Garra'bor = city on the island in the North-East of Khalinor\\
	Karra'bor = city in the North-East of Khalinor, population came from Garra'bor\\
	Maviara Bay = Bay in the North-East of Khalinor\\
	Mavior = City in Maviara Bay, at war with Aradar\\
	Aradar = City in Maviara Bay, at war with Mavior\\ 
	Valley of Death = dangerous valley in the North of Khalinor\\
	Orvik = only drarven overworld city located to the South-West of the mountains of Ghamor\\
	Bronzeforge = highest mountain of Ghamor\\
	the Great War = biggest war of Aminor, in year 0\\city
	Dragonscale = mountain of Ghamor, located in the West\\
	Thunderaxe = mountain of Ghamor, located in the South\\
	Stonecrusher = mountain of Ghamor, located in the North\\
	Draken Islands = islands in the North-West of Aminor\\
	Fey = big forest in the Greenlands\\
	Kara'ar tree = tree in the center of the Fey, holy to elves and eladrin\\
	Sowgill Lake = biggest lake in Aminor, located in the South of the Greenlands\\
	Ballick valley = valley in the north of the Greenlands. Filled to the brim with magic\\
	Grendale islands = islands south of the Greenlands, home to the richest of Aminor\\
	Aldskull = city in the North of the Greenlands, is in contact with the outpost on the Draken islands\\
	Kingsrend = capital of the Greenlands, located in the Ballick valley\\
	Linbrough =  ruling city of the southern third of the Greenlands\\
	Awalock = ruling city of the western third of the Greenlands\\
	Windwarder = city in the west of the Greenlands at the border to the Fey\\
	Blackwater = city in the east of the Greenlands, where the three big rivers flow together\\
	Alwador = city in the center of the Ballick valley, where the biggest of the two magic universities of Aminor lies\\
	Murakar = city in the south of the Ballick valley, with the oldest library of the contintent\\
	Boron = capital of the Grendale islands\\
	Baltar = northern island of the Grendale islands\\
	Bolar = western island of the Grendale islands\\
	Brunken = eastern island of the Grendale islands\\
	Bergar = southern island of the Grendale islands\\
	Plywell = city at the eastern coast of the Greenlands\\
	Caterick = city, at the mound of the Jall River\\
	Bellick = city at the mound of the Jall River\\
	Orvon = city at the border of the Fey, and Sogwill lake\\
	Bogrib = river in the east of the Greenlands\\
	Bildor Creek = river in the north of the Greenlands, flows out of the Ballick valley\\
	Jall River = biggest river in the Greenlands, mounds into Sogwill lake\\
	Blog River = river in the north of the Greenlands\\
\end{document}